Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2018-06-19 writeup/conStruct.tex
fixed postmerge typos

From a practical standpoint, even while acknowledging continuous
processes, we often need to identify somewhat separable populations 
from which individuals are sampled \cite{wright1949genetical}.
Delineating populations is useful for systematics and for
informing conservation priorities \cite{Moritz1994,Waples_1998,Moritz_etal_2002}.
Furthermore, we often need to identify subsets of indivduals resulting from reasonably coherent
evolutionary histories for downstream analyses to learn about population history and adaptation.
Conversely,
the substantial information available from continuous, geographic differentiation
(e.g., adaptation along a climatic gradient)
can be confounded by discrete historical processes (e.g., admixture),
requiring methods that can disentangle the two.

@@

We employ Monte Carlo cross-validation approach for model comparison \cite{picard1984}. 
This procedure generates a mean predictive accuracy for each model and each value of $K$, 
as well as a confidence interval around that mean,
which can then be used for model comparison or selection.
Briefly, we follow the following procedure:
\begin{enumerate}
\item For each of $X$ replicates:
	\begin{enumerate}
		\item partition the allele frequency data into a 90\% ``training'' partition ($F^x_1$) and a 10\%``testing" partition ($F^x_2$) \label{partition}

@@

In other words, the ``predictive accuracy'' shown as conStruct crossvalidation results
are in units of improvement in log-likelihood of that model relative to the best model for that partitioning of the data,
averaged over data partitions.
The standardization is necessary because different data partitions can be systematically 
more or less difficult to fit, resulting in greater differences in mean training data log likelihood 
between data partitions
than between models fit to the same partition.

>>>>

From a practical standpoint, even while acknowledging continuous
processes, we often need to identify somewhat separable populations 
from which individuals are sampled \cite{wright1949genetical}.
Delineating populations is useful for systematics and for
informing conservation priorities \cite{Moritz1994,Waples_1998,Moritz_etal_2002}.
Furthermore, we often need to identify subsets of individuals resulting from reasonably coherent
evolutionary histories for downstream analyses to learn about population history and adaptation.
Conversely,
the substantial information available from continuous, geographic differentiation
(e.g., adaptation along a climatic gradient)
can be confounded by discrete historical processes (e.g., admixture),
requiring methods that can disentangle the two.

@@

We employ a Monte Carlo cross-validation approach for model comparison \cite{picard1984}. 
This procedure generates a mean predictive accuracy for each model and each value of $K$, 
as well as a confidence interval around that mean,
which can then be used for model comparison or selection.
Briefly, we follow the following procedure:
\begin{enumerate}
\item For each of $X$ replicates:
	\begin{enumerate}
		\item partition the allele frequency data into a 90\% ``training'' partition ($F^x_1$) and a 10\%``testing" partition ($F^x_2$) \label{partition}

@@

In other words, the ``predictive accuracy'' shown as conStruct cross-validation results
are in units of improvement in log-likelihood of that model relative to the best model for that partitioning of the data,
averaged over data partitions.
The standardization is necessary because different data partitions can be systematically 
more or less difficult to fit, resulting in greater differences in mean training data log likelihood 
between data partitions
than between models fit to the same partition.
